Toward a More Accessible and Reproducible ISLS Conference Proceedings Paper: A Practical Workshop Using Cutting-Edge Tools

### 2021-01-09 paper_contents.tex
Fix line break in and typo

\section{Theme and goals}
The goal is for workshop participants to leave with a paper in either Overleaf, LaTeX, or Rmarkdown
As a theme, throughout the tutorial we will weave in what we believe are the four main advantages of using computational word processing approaches: crisp formatting, collaboration, reproducibility, and accessibility.

@@

\section{Additional Information}
\subsection{materials needed to participate}
Participants will need
	- Existing ISLS paper (or similar substitute)
	- Access to Rstudio (and dependant libraries)
	- Overleaf account

>>>>

\section{Theme and goals}

The goal is for workshop participants to leave with a paper in either Overleaf, LaTeX, or Rmarkdown. As a theme, throughout the tutorial we will weave in what we believe are the four main advantages of using computational word processing approaches: crisp formatting, collaboration, reproducibility, and accessibility.

@@

\section{Additional Information}
\subsection{materials needed to participate}
Participants will need
	- Existing ISLS paper (or similar substitute)
	- Access to Rstudio (and dependent libraries)
	- Overleaf account
